% !TEX TS-program = luatex
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/huajh/huajh-awesome-latex-cv
%
% Author:
% Junhao Hua
%
% Edited By:
% Hossein Beheshti

\documentclass[localFont]{awesome-source-cv} %alternative

\name{Hossein}{Beheshti}

\tagline{}
\socialinfo{
	\github{HosseinBeheshti}
	\linkedin{hosseinbeheshti} \\
	\smartphone{(+98) 912-488-96-64}
	\email{h.beheshti92@gmail.com} \\
	\address{Unit 3, No. 26, Jafari St, East Tehranpars, Tehran, Iran}\\
	\infos{23 Feb 1992, Tehran, Iran}
}

\begin{document}

\makecvheader


%----------------------------------------------------------------------------------------
%	ADDRESSEE AND GREETING
%----------------------------------------------------------------------------------------

\begin{tabular}{@{} l}
	Mrs.\ XXX           \\
	Recruitment Officer \\
	The Corporation     \\
	123 Pleasant Lane   \\
	City, State 12345
\end{tabular}

\bigskip % Vertical whitespace

Dear Mrs.\ XXX,

\bigskip % Vertical whitespace

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

PARAGRAPH ONE: State the reason for the letter, name the position or 
type of work you are applying for and identify the source from which 
you learned of the opening (i.e. career development center, newspaper, 
employment service, personal contact).

PARAGRAPH TWO: Indicate why you are interested in the position, the 
company, its products, services - above all, stress what you can do 
for the employer. If you are a recent graduate, explain how your 
academic background makes you a qualified candidate for the position. 
If you have practical work experience, point out specific achievements 
or unique qualifications. Try not to repeat the same information the 
reader will find in the resume. Refer the reader to the enclosed resume 
or application which summarizes your qualifications, training, and 
experiences. The purpose of this section is to strengthen your resume 
by providing details which bring your experiences to life.

PARAGRAPH THREE: Request a personal interview and indicate your 
flexibility as to the time and place. Repeat your phone number in 
the letter and offer assistance to help in a speedy response. For 
example, state that you will be in the city where the company is 
located on a certain date and would like to set up an interview. 
Alternatively, state that you will call on a certain date to set 
up an interview. End the letter by thanking the employer for 
taking time to consider your credentials.

\bigskip % Vertical whitespace
Best regards,
\vspace{50pt} % Vertical whitespace
Hossein Beheshti 
\end{document}

