\sectionTitle{Experiences}{\faBriefcase}

\begin{experiences}
	\experience
	{now} {FPGA Engineer}{Calnex Solutions plc}{Linlithgow, UK}
	{Dec 2022} {
		\begin{itemize}
			\item 
		\end{itemize}
	}
	{Networking, Embedded System, Agile Development}
	
	\emptySeparator
	
	\experience
	{Dec 2022} {FPGA Engineer, Product Owner}{SAMIM group}{Tehran,Iran}
	{Aug 2018} {
		\begin{itemize}
			\item Created and maintained product roadmap, planned 3-week sprints,
			      and prioritized team's backlog to provide a cohesive vision on
			      project goals aligned with business objectives, improving team
			      performance by $20\%$.
			\item Participated in developing the company's strategic plan for
			      next-generation 12G-SDI based products.
			\item Designed, implemented, and tested live production custom cores
			      such as Video Mixing, Format Conversion, Frame Synchronization,
			      and Audio Embedding/De-embedding.
			\item Implemented internal and board-level peripherals of FPGA, including
			      Gigabit Transceivers, DRAM interfaces,
			      standard protocols (SPI, I2C), Xilinx protocols, and video/audio
			      interfaces (SDI, BT1120, HDMI, AES3).
			\item Experienced with integrated embedded processors and custom IP cores
			      in SOC FPGA Design.
		\end{itemize}
	}
	{Broadcasting, Embedded System, PetaLinux, Agile Development, Gitlab CI/CD}
	
	\emptySeparator
	
	\experience
	{Jun 2018} {Research Assistant}{IUST}{Tehran,Iran}
	{Mar 2015} {
		\emph{Iran University of Science and Technology, Signal Processing Lab}
		\begin{itemize}
			\item Research new technologies and create new product development plans.
			\item Coordinate with other functional teams during the product's life
			      cycle and be responsible for and require design modifications.
			\item Experience optimizing the design segmentation for a target FPGA
			      and executing timing closure.
			\item Experienced with high-speed ($4$ GSPS) ADC and DAC converters
			      and Radio Frequency (RF) circuits.
			\item Design telecommunication algorithms and Implement DSP techniques
			      such as FFTs, FIRs, IIRs, and CICs using VHDL/SystemVerilog
			      or system generator.
		\end{itemize}
	}
	{Digital Signal Processing, Algorithms, Telecommunication, Gitlab CI/CD}
	
	\emptySeparator
	
	\experience
	{Feb 2015} {Research Engineer}{IPM}{Tehran,Iran}
	{Aug 2012} {
		\emph{Institute for Research in Fundamental Sciences, Brain Engineering Research Center}
		\begin{itemize}
			\item Participate in Brain-Machine Interface (BMI) projects using brain
			      signals of humans or non-human primates to control robotic platforms.
			\item Developed instruments for brain signal emulation/detection
			      with the collaborations of
			      neuroscientists and psychologists.
			\item Perform design verification tests, analyze results, provide
			      recommendations, and drive implementation.
		\end{itemize}
	}
	{Brain Signal Processing, Neuroscience, MATLAB, VIVADO}
	
	\emptySeparator
	
	\experience
	{Oct 2013} {Engineering Apprentice}{SBU}{Tehran,Iran}
	{May 2013} {
		\emph{Laser and Plasma Research Institute}
		\begin{itemize}
			\item FPGA implementation of polyphase 1:8 filter on Spartan-6 SP605 Evaluation Kit.
		\end{itemize}
	}
	{DSP, FPGA}
\end{experiences}
